Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-01-31 paper/main.tex
Updates

\begin{enumerate}
	\item \textbf{Bounded: } $ \rho $ is bounded between $ 0 $ and $ 1 $,
		with $ 0 $ representing no association while $ 1 $ represents
		perfect linear association. This helps in interpretation and
		comparing values across multiple partial associations.
	\item \textbf{Independent of Sample Size: } The measure remains consistent
		regardless of the sample size ensuring reliability across 
		studies with different sample sizes.
	\item \textbf{Invariant to the Dummy Encoding Scheme: } Since canonical
		correlations search for linear combinations over the columns,
		the measure is invariant to the specific dummy encoding
		scheme used for categorical variables.
	\item \textbf{Generalizes Partial Correlations to Mixed Data: }
		Canonical correlations is equivalent to Pearson's correlation coefficient
		when both $ X $ and $ Y $ are continuous. Hence, $ \rho $ generalizes
		partial correlations to mixed data types.
	\item \textbf{Related to Cramer\'s V: } 
\end{enumerate}

@@

\section{Using Measure of Association for DAG Modification and Construction}
\label{sec:modification}

@@

\todo[inline]{Add a figure showing an example of how this modification works.}

>>>>

\begin{enumerate}
	\item \textbf{Bounded: } $ \rho $ is bounded between $ 0 $ and $ 1 $,
		with $ 0 $ representing no association while $ 1 $ represents
		perfect linear association. This helps in interpretation and
		comparing values across multiple partial associations.
	\item \textbf{Independent of Sample Size: } The measure remains consistent
		regardless of the sample size ensuring reliability across 
		studies with different sample sizes.
	\item \textbf{Invariant to the Dummy Encoding Scheme: } Since canonical
		correlations search for linear combinations over the columns,
		the measure is invariant to the specific dummy encoding
		scheme used for categorical variables.
	\item \textbf{Generalizes Partial Correlations to Mixed Data: }
		Canonical correlations is equivalent to Pearson's correlation coefficient
		when both $ X $ and $ Y $ are continuous. Hence, $ \rho $ generalizes
		partial correlations to mixed data types.
	\item \textbf{Generalizes polychoric and polyserial correlation: }
		Under the assumption that the ordinal variable is generated by
		discretizing an underlying gaussian continuous variable, this
		effect size is equivalent to polychoric and polyserial
		correlation. As both of them recover the Pearson correlation
		coefficient.
	\item \textbf{Related to Cramer\'s V: } 
\end{enumerate}

@@

\section{Using Measure of Association for DAG Construction}
\label{sec:modification}

@@
